---
title: "Homework 4"
author: "Chunjin Ruan"
date: "Due by 2:20 pm, Fri. 2/15"
output: github_document
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```


Push your knitted homework assignment (.Rmd and .md files) to GitHub by the given deadline.

Also let me know: 

**Who you worked with:**

### Problem 1
The vector called `words` in `stringr` contains a corpus of 980 words used in text analysis.  Use regular expressions with `stringr` to find the words that satisfy the following descriptions: 

- begin with `b`
- contain `q`, `x`, or `z`
- contain `th` or `ch`
- end with `g` but not `ng`
- are 10 letters long
- have 3 or more vowels in a row
- start and end with the same letter

```{r}
library(tidyverse)
library(readr)
library(stringr)
library(rvest)
library(ggrepel)
```
####begin with `b`
```{r}
words %>%
  subset(str_detect(words, "^b"))
```
####contain `q`, `x`, `z`
```{r}
words %>%
  subset(str_detect(words, "q|x|z"))
```
####contain `th` or `ch`
```{r}
words %>%
  subset(str_detect(words, "th|ch"))
```
#### end with `g` but not `ng`
```{r}
words %>%
  subset(str_detect(words, "[^n]g$"))
```
####are 10 letters long
```{r}
words %>%
  subset(str_detect(words, "^.{10}$"))
```
####have 3 or more vowels in a row
```{r}
words %>%
  subset(str_detect(words,"[aeiouy]{3,}"))
```
####start and end with the same letter
```{r}
words %>%
  subset(str_detect(words, "^(.).*\\1$"))
```


### Problem 2

Revisit the `words` vector. What word, or words, in this vector has the highest number of vowels? What word has the highest proportion of vowels?

```{r}
library(stringr)
words <- as.tibble(words)
words %>%
  mutate(vowels = str_count(value, "[aeiouy]")) %>%
  filter(vowels == max(vowels)) 
```
**Answer** appropriate, associate, authority, available, colleague, encourage, experience, individual, opportunity, television are the highest number of vowels. 
```{r}
words %>%
  mutate(vowels = str_count(value, "[aeiouy]")) %>%
  mutate(prop_vowels = vowels /str_length(value)) %>%
  arrange(desc(prop_vowels))
```
**Answer** a, eye, you are the highest number of vowels. 
### Problem 3

(Combining exercise 15.6 and 15.7)

Project Gutenberg contains the full text of *The Complete Works of William Shakespeare*. (http://www.gutenberg.org/files/100/100-0.txt)


**(a)** Use the `read_lines()` in **readr** to import the text data.
```{r}
shakespeare <-read_lines("http://www.gutenberg.org/files/100/100-0.txt")
```

**(b)** Use regular expressions to determine the number of speaking lines in *The Complete Works of William Shakespeare*.  Speaking lines in Shakespeare’s plays are identified by a line that starts with two spaces, then a string of capital letters and spaces (the character’s name) followed by a period. Here, we care only about how many times a character speaks—not what they say or for how long they speak.

```{r}
lines <-shakespeare %>%
  subset(str_detect(shakespeare, "^\\s\\s[A-Z]+[A-Z\\s]+[.]"))
length(lines)
```
**Answer** There are 19965 speaking lines in Shakespeare's plays are identified.

**(c)** Make a bar chart displaying the top 100 characters with the greatest number of lines. *Hint:* you may want to use either the `str extract()`.
####Extract names and find the occurrance of the names 
```{r}
shakespeare <-as_tibble(shakespeare)
shakespeare %>%
  filter(str_detect(value, "^\\s\\s[A-Z]+[A-Z ]+[.]")) %>%
  separate(value, into = c("name", "line"), sep = "[.]") %>%
  group_by(name) %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  slice(1:100) %>%
  ggplot(aes(x = fct_reorder(name, -count), y = count)) +
  geom_col() +
  labs(title = "The top 100 characters with the greatest number of lines", x = "character", y = "number of lines")
  
```

### Problem 4

Scrape the table of data found at https://en.wikipedia.org/wiki/List_of_United_States_cities_by_crime_rate and create a plot showing violent crime rate (total violent crime) vs. property crime rate (total property crime).  Identify outlier cities by using a plotting command such as:

```{r}
#Load data
tables <-read_html("https://en.wikipedia.org/wiki/List_of_United_States_cities_by_crime_rate") %>%
  html_nodes("table") 
#Check the tables
crimes_table1 <- html_table(tables[[1]])
crimes_table2 <- html_table(tables[[2]], fill = TRUE)
crimes_table3 <- html_table(tables[[3]])

crime <-crimes_table2[c(1,2,4,9)]
crime <- crime %>%
  as.tibble() %>%
  slice(-1) %>% 
  rename(vio_crime = "Violent Crime",
         prop_crime = "Property Crime")
crime$vio_crime <- as.numeric(crime$vio_crime)
crime$prop_crime <- as.numeric(crime$prop_crime)
```

```{r}
ggplot(crime, aes(x = vio_crime, y = prop_crime, label = City)) +
    geom_point() +
    geom_label_repel(data=subset(crime, vio_crime > 1500 | prop_crime > 6500), 
              check_overlap = TRUE, size = 2.5, nudge_y = 200) + 
    labs(title = "Violent crime rate vs. property crime rate", x = "violent crime rate", y = "property crime rate")
```

Hints:

- after reading in the table using `html_table()`, create a data frame with just the columns you want using column numbers.  Otherwise, R gets confused since it appears as if several columns all have the same column name.
- then, turn `crimes` into a tibble with `as.tibble(crimes3)` and do necessary tidying: get rid of unneeded rows, parse columns into proper format, etc.

Alternatives to `geom_text()`:

If you want to try something new, check out the **ggrepel** package to label the outliers.

### Problem 5

Scrape the data from IMDB's top grossing films released in 2018 at https://www.imdb.com/search/title?year=2018&title_type=feature&sort=boxoffice_gross_us,desc.  Create a tibble that contains the title, gross, imdbscore, and metascore for the top 50 films.  Then generate a scatterplot of one of the ratings vs. gross, labeling outliers as in Problem 4 with the title of the movie.

```{r}
website <- read_html("https://www.imdb.com/search/title?year=2018&title_type=feature&sort=boxoffice_gross_us,desc") 
movie_title <- website %>%
  html_nodes(".lister-item-header") %>%
  html_text() %>%
  parse_character()

movie_gross <- website %>%
  html_nodes(".sort-num_votes-visible") %>%
  html_text() 

movie_imdbscore <- website %>%
  html_nodes(".ratings-bar") %>%
  html_text()

movie_info <- tibble(
  title = movie_title,
  gross = movie_gross,
  imdbscore = movie_imdbscore
)

movie_info1 <-movie_info %>%
  separate(title, into = c("title", "year"), sep = "[(]\\d{4}") %>%
  separate(gross, into = c("vote", "gross"), sep = "[$]") %>%
  separate(imdbscore, into = c("imdbscore", "metascore"), sep = "Rate") %>%
  separate(metascore, into = c("what", "metascore"), sep = "X") %>%
  mutate(title = str_remove_all(title, "\n"),
         title = str_trim(title),
         gross = parse_number(gross),
         imdbscore = parse_number(imdbscore),
         metascore = parse_number(metascore)
         )
movie_info1 %>%
  separate(title, into = c("number", "title"), sep = "[.]") %>%
  ggplot(aes(x = imdbscore, y = gross)) +
  geom_point() +
  geom_label_repel(data=subset(movie_info1, imdbscore > 8 | gross > 450),
                   aes(label = title),
              check_overlap = TRUE, size = 2.5, nudge_y = 2) +
  labs(title = "The scatterplot of imdbscore by gross income",y = "Gross income(in millions)", x = "imdb score")
```


